\section{Shared Part}

This could be the Shared Part of the document. It is designed to be written by all members of the team.

Each member should ideally write their details in the table of contributors in the Shared Part of the document.



\subsection{Comments from the second student}
This is the first subsection. Do not forget to include the best parts about the module as well as what you did not like about Max Wilson during the term.

\subsection{Comments from the third student}
The best part of this term was the man-eating anteater attack. I did not like the fact Max used students as a human shield to protect himself during this trying time and I feel his feedback to the students that fought and died so valiantly could have been more constructive. However this was redeemed by the large donations he made in their names to anti-mad-scientist causes. 

\subsection{Comments from the forth student}
This is the first subsection. Do not forget to include the best parts about the module as well as what you did not like about Max Wilson during the term.

\subsection{Comments from the fifth student}
This is the first subsection. Do not forget to include the best parts about the module as well as what you did not like about Max Wilson during the term.

\subsection{Table of Contributors}


If you want to move a table around you will need to put some parameters in square brackets, if you want it exactly where it is positioned in the text editor just uncomment the [h] below, just after begin{table}

This is the table of contributors (Table~\ref{authors}):
\begin{table}%[h]
\centering
\caption{People in the Group}
\label{authors}
\begin{tabular}{|l|l|}
\hline
\textbf{Name} & \textbf{ID} \\
\hline
& \\
\hline
& \\
\hline
Alexi & psyajd \\
\hline
& \\
\hline
James Cordon & psyjmc \\
\hline
\end{tabular}
\end{table}